\documentclass{article}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{
  amssymb,
  amsmath,
  amsthm,
  latexsym
}
\graphicspath{{./images/}}
\title{Analysis of Lawns Lab Report}
\author{Philip Kim}
\date{\today}
\begin{document}
\begin{enumerate}
  \item Compare the lines for the two lawns. Were the patterns similar or different in the two lawns? How so?
  \begin{itemize}
    \item \textbf{Disturbed lawn species}: more L-shaped curve, less number of richness \& evenness, lower Shannon Index Value.
    \item \textbf{Undisturbed lawn species}: more flat curve, more number of richness \& evenness, higher Shannon Index Value.
  \end{itemize}
  \item Did the two lawns that your class surveyed have similar or different species richnesses? Give the species richness of each lawn. (Species richness = \# of different species represented; it is simply the species count)
  \begin{itemize}
    \item \textbf{Disturbed lawn species richness}: \(\boxed{9}\)
    \item \textbf{Undisturbed lawn species richness}: \(\boxed{12}\)
  \end{itemize}
  \item Compare the two lawns’ Shannon index values. Which lawn has more diversity of broad-leafed (non-grass) plants? (The higher the Shannon index value, the higher the species richness and evenness)
  \begin{itemize}
    \item \textbf{Disturbed lawn Shannon Index Value}: \(\boxed{0.796200234}\)
    \item \textbf{Undisturbed lawn Shannon Index Value}: \(\boxed{1.246039233}\)
    \item Undisturbed lawn had more diversity of broad-leafed (non-grass) plants.
  \end{itemize}
\end{enumerate}
\end{document}


